How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2021-01-04 analysis/paper/paper.Rmd
added citation and SPD figure/ title inside

There is a debate about whether past population growth has played a role in technological change [@shennan2001demography; @kline2010population]. @shennan2009pattern observed a correlation between population decrease and technological simplification in their study of lithic arrowheads from the southern Scandinavian Mesolithic. They found that the lithics became less complex, and point shape changed as the population level dropped. On the other hand, @collard2013population argue that regional archaeological data do not support the population-driven models [@buchanan2016drivers]. For example, @buchanan2016drivers concluded that changes in point types from \>13,000 years ago to 400 years ago in Texas were related to environmental risk, and not dependent on population size. We explored SPD to test for correlations between population, environmental risk and technological change. We used the R package 'rcarbon' [@cremaanalysing] to perform statistical analyses and conduct model testing using Monte Carlo methods. We generated exponential, uniform, linear, and logistic models and evaluated the model goodness-of-fit by applying Akaike's Information Criterion (AIC) as a selection criterion [@sakamoto1986akaike; @bevan2017holocene; @riris2019widespread].

>>>>

There is a debate about whether past population growth has played a role in technological change [@shennan2001demography; @kline2010population]. @shennan2009pattern observed a correlation between population decrease and technological simplification in their study of lithic arrowheads from the southern Scandinavian Mesolithic. They found that the lithics became less complex, and point shape changed as the population level dropped. On the other hand, @collard2013population argue that regional archaeological data do not support the population-driven models [@buchanan2016drivers]. For example, @buchanan2016drivers concluded that changes in point types from \>13,000 years ago to 400 years ago in Texas were related to environmental risk, and not dependent on population size. We explored SPD to test for correlations between population, environmental risk and technological change. We used the R package 'rcarbon' [@cremaanalysing] to perform statistical analyses and conduct model testing using Monte Carlo methods [@timpson2014reconstructing; @crema2016summed; @palmisano2020holocene]. We generated exponential, uniform, linear, and logistic models and evaluated the model goodness-of-fit by applying Akaike's Information Criterion (AIC) as a selection criterion [@sakamoto1986akaike; @bevan2017holocene; @riris2019widespread].
